\documentclass[xcolor=svgnames,handout]{beamer}

\usepackage[utf8]    {inputenc}
%\usepackage[T1]      {fontenc}
\usepackage[english] {babel}

\usepackage{amsmath,amsfonts,graphicx}
\usepackage{beamerleanprogress}
\usepackage{hyperref}
\usepackage{bookmark}
\bookmarksetup{startatroot}

\title[FAA\hspace{2em}]{(FL)~OSS \& Art}

\author[Theodore Se\'{a}n Tubbs]{Theodore Se\'{a}n Tubbs}

\date{\today}

\institute{DCMO BOCES}

\setbeamertemplate{navigation symbols}{\insertframenavigationsymbol{}\insertsectionnavigationsymbol{}\insertbackfindforwardnavigationsymbol{}}
% navigational symbols
\begin{document}

\maketitle

\section{Introduction}
\subsection{Table of Contents}
\begin{frame}
  {Table of Contents}

\tableofcontents
%  Topics\pause

%  \begin{itemize}
%  \item What is FLOSS?\pause
%  \begin{enumerate}
%	  \item{My background with FLOSS}
%	  \item{FLOSS/other Licenses}
%	  \item{Examples of OSS in the graphics design industry}
%  \end{enumerate}
%  \item What does it have to do with art?\pause
%	  \begin{enumerate}
%		  \item{My background in ``art''}
%		  \item{The art community (what I've seen)}
%		  \item{The future? (it is looking brighter!)}
%	  \end{enumerate}
%
%  \item{Conclusion}
%  \end{itemize}
\end{frame}



\section{What is FLOSS?}

\begin{frame}
	{What is FLOSS?}
	\begin{itemize}
		\item Breaking FLOSS down
		\item My background with FLOSS
		\item OSS in the graphics design industry
	\end{itemize}

\end{frame}

\subsection{Breaking FLOSS down}
\begin{frame}{Breaking FLOSS down}

\href{https://www.gnu.org/philosophy/free-sw.en.html}{FLOSS}
\begin{itemize}
  \item F\@: Free
	  \begin{itemize}
		  \item Free as in speech, not as in beer!
	  \end{itemize}
  \item L\@: Libre
  \item O\@: Open
  \item S\@: Source
  \item S\@: Software
  \item Be aware though, open-source != FLOSS
  \end{itemize}
\end{frame}

\subsection{My background with FLOSS}
\begin{frame}{My background with FLOSS}

	\begin{itemize}
		\item Long time GNU/Linux user
			\begin{itemize}
				\item 3--4 years
				\item The distro I use is Lubuntu
			\end{itemize}
		\item \href{https://github.com/AdrianKoshka}{I've used github for 3-4 years}
			\begin{itemize}
				\item I have a repository where my academic and creative papers go
					\begin{itemize}
				\item Most of the docs I write are either \LaTeX, or markdown
					\end{itemize}
				\item I helped bootstrap documentation for OpenIndiana
				\item I have made my own `.Xresources' colourschemes
				\item I have other various repos, both source and forks
			\end{itemize}
		\item I've contributed in small ways to the iPXE project
		\item Other small tidbits I probably forgot
	\end{itemize}
\end{frame}

\subsection{OSS in the graphics design industry}
\begin{frame}{OSS in the graphics design industry}

	\begin{itemize}
		\item AMD
			\begin{itemize}
				\item \href{http://gpuopen.com/games-cgi/}{GPUOpen}
			\end{itemize}
		\item Blackmagicdesign
			\begin{itemize}
				\item \href{https://www.blackmagicdesign.com/products/fusion}{Fusion}
			\end{itemize}
		\item \href{https://www.blender.org/}{Belnder\textsuperscript{\texttrademark}}
		\item Intel\textsuperscript{\textregistered}
			\begin{itemize}
				\item \href{https://01.org/linuxgraphics}{GPU drivers for GNU/Linux}
			\end{itemize}
		\item Khronos\textsuperscript{\texttrademark} Group
			\begin{itemize}
				\item \href{https://www.khronos.org/members/contributors}{Vulkan\textsuperscript{\texttrademark}}
			\end{itemize}
		\item \href{https://krita.org/en/}{Krita}
		\item Pixar
			\begin{itemize}
				\item \href{https://github.com/PixarAnimationStudios/USD}{Universal Scene Description (USD)}
			\end{itemize}
		\item Studio Ghibli
			\begin{itemize}
				\item \href{https://opentoonz.github.io/e/}{OpenToonz}
			\end{itemize}
	\end{itemize}

\end{frame}

\section{What does it have to do with art?}

\begin{frame}{What does it have to do with art?}

	\begin{itemize}
		\item My background in ``art''
		\item The art community (what I've seen)
		\item The future? (it is looking brighter!)
	\end{itemize}

\end{frame}

\subsection{My background in ``art''}

\begin{frame}{My background in ``art''}
	\begin{itemize}
		\item I use \LaTeX{} and Markdown (So Typography I guess?)
		\item I helped in bootstraping documentation for OpenIndiana
			\begin{itemize}
				\item Technical docs are harder then you think!
				\item Alot has to go into the docs, such as:
					\begin{itemize}
						\item How will you present the docs?
						\item What software will the document writes use?
						\item What will the documentation look like?
						\item How much detail do you put into the docs?
						\item Will you provide these docs in many formats?
						\item So on and so forth\ldots
					\end{itemize}
				\item I have an interest in Photography and Cinematography
			\end{itemize}
	\end{itemize}
\end{frame}

\subsection{The art community (what I've seen of it)}

\begin{frame}
	{The art community (what I've seen of it)}

	\begin{itemize}
		\item DISCLAIMER\@:
			\begin{itemize}
				\item I'm doing this off my limited knowledge!
				\item Disney rant
			\end{itemize}
		\item Disney ruined Copyright and IP, and will continue to do so!
			\begin{itemize}
				\item They don't want anything to be public domain EVER\@!
				\item They don't want others to profit from their works.
				\item They want to keep Mickey Mouse prisoner forever!
				\item I'm sorry, I just had to mention these guys
			\end{itemize}
		\item I'm not really gonna put things about the art community here.
			\begin{itemize}
				\item I don't want to make broad statements on paper
				\item I'd rather converse with artists about this
				\item Please don't hurt me artists!
			\end{itemize}
	\end{itemize}

\end{frame}

\subsection{The future? (it is looking brighter!)}

\begin{frame}
	{The Future? (it is looking Brighter!)}

	\begin{itemize}
		\item Huge companies/groups are open-sourcing their tools!
		\item More artists are using open-source tools!
		\item Maybe one day Adobe will fall!

	\end{itemize}


\end{frame}

\section{Conclusion}
\subsection{Credits}

\begin{frame}
  {Credits}

  \begin{itemize}
  \item Template made by: Cédric Mauclair
  \item Free Software Foundation: for info about FLOSS
  \item Various \TeX{} stackexchange posts on how to do stuff
  \item Wikibooks: how do certain other things with \LaTeX{}
  \item Other people/things I probably forgot to mention!
  \end{itemize}
\end{frame}

\end{document}
